Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations

### 2021-05-10 papers/intro_paper/intro_paper.tex
changes

Ground-based detectors, such as LIGO and Virgo, are most sensitive to
stellar-mass BH binaries that form remnants with mass $\gtrsim 50 M_{\odot}$ and merge near the
minimum of their sensitivity band ($\sim 100$ Hz). As a consequence, the
remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving
very little signal-to-noise ratio (SNR) in the
post-merger signal. Most of the tests mentioned above restrict the data to this post-merger signal which, while being agnostic to deviations in the pre-merger dynamics, significantly reduces parameter-estimation capabilities. Added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}). \textcolor{blue}{Defining such a time is particularly important in order to avoid possible systematic errors that may occur if one tries to apply perturbation theory in a regime where non-linearities are still important}. In some tests~\cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time has been left as a free parameter to be estimated directly from the data. Whereas, in other cases, the ringdown start time is predicted from corresponding full-signal parameter-estimation analyses (see \texttt{pyRing} analysis in Ref.~\cite{Abbott:2020jks}). Uncertainties
in estimates of the ringdown start-time, as well as an overall lack of
SNR in the post-merger signal, given typical sensitivities of
ground-based detectors, can result in significant statistical uncertainties in the measurement of some of the QNM properties. This is especially true for the measurement of the QNM damping times which are, in general, harder to measure from the data. Hence, one might want to look at alternate methods to measure QNMs using information from as much as the signal as possible.

>>>>

%Ground-based detectors, such as LIGO and Virgo, are most sensitive to stellar-mass BH binaries that form remnants with mass $\gtrsim 50 M_{\odot}$ and merge near the minimum of their sensitivity band ($\sim 100$ Hz). As a consequence, the remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving very little signal-to-noise ratio (SNR) in the post-merger signal. 
\textcolor{blue}{With current ground-based detectors, only a small fraction of BBH coalescences lead to a detectable post-merger GW signal and, even for these events, the signal-to-noise ratio (SNR) in the post-merger signal is, in most cases, only slightly above threshold for detection~\cite{LIGOScientific:2019fpa,Abbott:2020jks}. This is likely to remain the case in the near future~\cite{Berti:2016lat}.}
%
\textcolor{blue}{This is particularly important, given that} most of the tests mentioned above restrict the data to this post-merger signal which, while being agnostic to deviations in the pre-merger dynamics, significantly reduces parameter-estimation capabilities. Added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}). \textcolor{blue}{Defining such a time is particularly important in order to avoid possible systematic errors that may occur if one tries to apply perturbation theory in a regime where non-linearities are still important}. In some tests~\cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time has been left as a free parameter to be estimated directly from the data. Whereas, in other cases, the ringdown start time is predicted from corresponding full-signal parameter-estimation analyses (see \texttt{pyRing} analysis in Ref.~\cite{Abbott:2020jks}). Uncertainties
in estimates of the ringdown start-time, as well as an overall lack of
SNR in the post-merger signal, given typical sensitivities of
ground-based detectors, can result in significant statistical uncertainties in the measurement of some of the QNM properties. This is especially true for the measurement of the QNM damping times which are, in general, harder to measure from the data. Hence, one might want to look at alternate methods to measure QNMs using information from as much as the signal as possible.
